Revisiting some definitions with common examples from Gregorian calendar

### 2019-12-05 CyclicGran.Rmd
demystifying defintions

---
title: Revisiting some definitions with common examples from Gregorian calendar
author: Sayani Gupta
branding: FALSE
fontfamily: mathpazo
output: pdf_document
---

@@

The concept already existed in the literature. This is an attempt to demistify the notations using the linear granularities day and month.

@@

\begin{equation}\label{eq:eq1}
\begin{split}
month(0) & = day(0)\bigcup day(1)\dots\bigcup day(30)\\
month(1) & = day(31)\bigcup day(32)\dots\bigcup day(58)\\
month(2) & = day(59)\bigcup day(60)\dots\bigcup day(89)\\
\dots\\
month(11) & = day(334)\dots day(363)\bigcup day(364)\\
\end{split}
\end{equation}

@@

Generalizing it to any two linear granularities G and H , the formal way of defining the property "groups periodically into" would like the following:

\newtheorem{definition}{Definition}
\begin{definition}\label{def:periodical}
A granularity H is periodical with respect to a granularity G if
(1) $G \trianglelefteq H$, and
(2) there exist $R,P \epsilon Z+$, where R is less than the number of granules of H, such
that for all $j \epsilon Z$, if $H(j) = \bigcup_{i \in S}G(i)$ and $H (j + R) \neq \phi$ then
$H (j + R) = \bigcup_{i \in S} G(i + P)$.
\end{definition}

@@

Here, ${S_0,...,S_{11}}$ are the sets of indexes of G describing $month(0), . . . , month(11)$. Then from Definition \autoref{def:periodical}, it also follows that if $H$ is periodical with respect to $G$, then

\begin{equation}\label{eq:eq4}
H(j) = \bigcup_{i \in S_j \mod R}G(P*\lfloor j/R \rfloor + i)
\end{equation},

where ${S_0,...,S_{R-1}}$ are the sets of indexes of G describing $H (0), . . . , H (R - 1)$ respectively. Here $j \mod R$ represents the index among those in ${0, 1, \dots, R-1}$ that must be shifted to obtain $H(j)$. The number of periods each granule of G composing $H(j \mod R)$ should be shifted is given by $\lfloor j/R\rfloor$.

Thus,  to obtain $month(13)$ in terms of days we can either use Definition \autoref{def:periodical} or \autoref{eq:eq4}
\begin{equation}
\begin{split}
month(13) & =  month (1 + 12)\\
 & = \bigcup_{i \in S_1} day(i + 365) \quad since \quad month(1) =  \bigcup_{i \in S_1}day(i), \quad S_1 = {31, 32, \dots, 58}\\
 & = day(31 + 365)\bigcup day(32 + 365)\bigcup day(58 + 365)\\
\end{split}
\end{equation}

@@

\begin{definition}\label{def:circular}
A circular granularity C(B, G) relates a linear granularity G to the bottom granularity B, if

\begin{equation} \label{eq:eq2}
\begin{split}
C_{B, G}(z) & = {L}(z\mod P) \quad \forall z \in \mathbb{Z}^+ \\
\end{split}
\end{equation}
where,
z denotes the index set,
B denotes a full-integer labelled bottom granularity which groups periodically into linear granularity G with regular mapping, 
{L} is a label mapping that defines an unique label for each index $l \in {0,1,\dots, (P-1)}$,
and P is the number of granules of B in each granule of G.
\end{definition}

@@

A **quasi-circular** granularity can not be defined using modular arithmetic due to its irregular mapping with the bottom granularity. Here $P/R \not \in \mathbb{Z}^+$. However, they are still formed with linear granularities, one of which "groups periodically into" the other. We shall discuss an example of  quasi-circular granularity day-of-month in \autoref{fig:quasi-circular-explain}. The index 34 should correspond to L(3) which is "4th-day-of-month", that of 60 should correspond to L(1), which is "2nd-day-of-month" and 334 should correspond to L(0), which is "1st-day-of-month". Now, quasi-circular granularities can be defined as follows to obtain these labels:

@@

\begin{equation}\label{eq:eq3}
Q_{B, G'}(z) = L(z - \sum_{w=0}^{k-1}\vert T_{w \mod R'} \vert), \quad z \in T_k
\end{equation}

where,  
$z$ denotes the index set,
$B$ denotes a full-integer labelled bottom granularity which groups periodically into linear granularity $G'$ with irregular mapping, {L} is a label mapping that defines an unique label for each index $l \in {0,1,\dots, (k-1)}$, $T_w$ are the sets of indices of B describing $G'(w)$ such that 
\begin{equation}
G'(w) = \bigcup_{z \in T_w}B(z),\\
\end{equation}
$T_w = 0 \quad for \quad w\epsilon Z_{<0}$ and $\vert T_w \vert$ is the cardinality of set $T_w$.
\end{definition}

@@

\begin{equation}
\begin{split}
Q_{day, month}(34) & = L(35 - 31) \quad since \quad 35 \in \quad month(1)\\
Q_{day, month}(60) & = L(60 - 31 - 28), \quad since\quad 60 \in \quad month(2)\\
Q_{day, month}(334) & = L(334 - 334) \quad since \quad 334 \in \quad month(11)\\
\end{split}
\end{equation}.

@@

\begin{definition}\label{aperiodic}
An aperiodic granularity $A_{B, G''}$ that relates linear granularities G and bottom granularity $B$, with $G''$ being aperiodical with respect to $B$, is given by

\begin{equation}\label{eq:eq4}
\begin{split}
A_{B, G''}(z) & = L(1), \quad z \in T_q\\
     & = L(0), \quad z \not\in T_q\\
\end{split}
\end{equation}
where  
$z$ denotes the index set,
$T_q$ are the sets of indices of $B$ describing $G''(q)$ such that $$G''(q) = \bigcup_{z \in T_q}B(z)$$
\end{definition}

 Aperiodic time granularities map a time index to binary categories. It takes the value 1 whenever the time index coincides with the events in context (e.g. public or school holiday) and 0 when it does not. \autoref{fig:aperiodic} shows the linear granularity academic semester and days. Academic semesters are not periodic with respect to days. The label mapping L can be defined as $L: ({0,1}) \longmapsto\ ({On, Off)}$ or can be customised based on context.

>>>>

---
title: Revisiting some definitions with common examples from Gregorian calendar
author: Sayani Gupta
branding: FALSE
fontfamily: mathpazo
output:
  MonashEBSTemplates::memo:
    keep_tex: true
header-includes:
  - \usepackage[lf,t]{carlito}
  - \titleformat{\section}[block]{\fontsize{12}{14}\bfseries\sffamily}{\thesection}{0.4em}{}
  - \def\mod{\text{~mod~}}
---

@@

The concept already existed in the literature. This is an attempt to demystify the notations using the linear granularities day and month.

@@

\begin{equation}\label{eq:eq1}
\begin{split}
month(0) & = day(0)\bigcup day(1)\dots\bigcup day(30)\\
month(1) & = day(31)\bigcup day(32)\dots\bigcup day(58)\\
month(2) & = day(59)\bigcup day(60)\dots\bigcup day(89)\\
\dots\\
month(11) & = day(334)\dots day(363)\bigcup day(364)\\a
\end{split}
\end{equation}

@@

Generalizing it to any two linear granularities $G$ and $H$ , the formal way of defining the property "groups periodically into" would like the following:

\newtheorem{definition}{Definition}
\begin{definition}\label{def:periodical}
A granularity H is periodical with respect to a granularity $G$ if
(1) $G \trianglelefteq H$, and \\
(2) there exist $R,P \epsilon Z+$, where R is less than the number of granules of H, such
that for all $j \epsilon Z$, if $H(j) = \bigcup_{i \in S}G(i)$ and $H (j + R) \neq \phi$ then
$H (j + R) = \bigcup_{i \in S} G(i + P)$.
\end{definition}

@@

Here, ${S_0,...,S_{11}}$ are the sets of indexes of $G$ describing $month(0), . . . , month(11)$. Then from Definition \autoref{def:periodical}, it also follows that if $H$ is periodical with respect to $G$, then

\begin{equation}\label{eq:eq4}
H(j) = \bigcup_{i \in S_j \mod R}G(P*\lfloor j/R \rfloor + i), 
\end{equation},

where ${S_0,...,S_{R-1}}$ are the sets of indexes of $G$ describing $H (0), . . . , H (R - 1)$ respectively. Here $j \mod R$ represents the index among those in ${0, 1, \dots, R-1}$ that must be shifted to obtain $H(j)$. The number of periods each granule of $G$ composing $H(j \mod R)$ should be shifted is given by $\lfloor j/R\rfloor$.

Thus,  to obtain $month(13)$ in terms of days we can either use Definition \autoref{def:periodical} or \autoref{eq:eq4}

\begin{equation}
\begin{split}
month(13) & =  month (1 + 12)\\
 & = \bigcup_{i \in S_1} day(i + 365) \quad since \quad month(1) =  \bigcup_{i \in S_1}day(i), \quad S_1 = {31, 32, \dots, 58}\\
 & = day(31 + 365)\bigcup day(32 + 365)\bigcup day(58 + 365)\\
\end{split}
\end{equation}

@@

\begin{definition}\label{def:circular}
A circular granularity C(B, G) relates a linear granularity $G$ to the bottom granularity B, if

\begin{equation} \label{eq:eq5}
\begin{split}
C_{B, G}(z) & = {L}(z\mod P) \quad \forall z \in \mathbb{Z}^+ \\
\end{split}
\end{equation}
where
z denotes the index set,
B denotes a full-integer labelled bottom granularity which groups periodically into linear granularity $G$ with regular mapping, 
{L} is a label mapping that defines an unique label for each index $l \in {0,1,\dots, (P-1)}$,
and P is the number of granules of B in each granule of G.
\end{definition}

@@

A **quasi-circular** granularity can not be defined using modular arithmetic due to its irregular mapping with the bottom granularity. However, they are still formed with linear granularities, one of which "groups periodically into" the other. We shall discuss an example of  quasi-circular granularity day-of-month in \autoref{fig:quasi-circular-explain}. The index 34 should correspond to L(3) which is "4th-day-of-month", that of 60 should correspond to L(1), which is "2nd-day-of-month" and 334 should correspond to L(0), which is "1st-day-of-month". Now, quasi-circular granularities can be defined as follows to manipulate the indices to our need:

@@

\begin{equation}\label{eq:eq6}
Q_{B, G'}(z) = L(z - \sum_{w=0}^{k-1}\vert T_{w \mod R'} \vert), \quad z \in T_k
\end{equation}

where
$z$ denotes the index set,
$B$ denotes a full-integer labelled bottom granularity which groups periodically into linear granularity $G'$ with irregular mapping, {L} is a label mapping that defines an unique label for each index $l \in {0,1,\dots, (k-1)}$, $T_w$ are the sets of indices of B describing $G'(w)$ such that 
\begin{equation}
G'(w) = \bigcup_{z \in T_w}B(z),\\
\end{equation}
$T_w = 0 \quad for \quad w\epsilon Z_{<0}$ and $\vert T_w \vert$ is the cardinality of set $T_w$.
\end{definition}

@@

\begin{equation}
\begin{split}
Q_{day, month}(34) & = L(34 - 31)       = L(3) \quad since \quad 35 \in \quad month(1)\\
Q_{day, month}(60) & = L(60 - 31 - 28)  = L(2) , \quad since\quad 60 \in \quad month(2)\\
Q_{day, month}(334) & = L(334 - 334)    = L(0) \quad since \quad 334 \in \quad month(11)
\end{split}
\end{equation}.

@@

\begin{definition}\label{aperiodic}
An aperiodic granularity $A_{B, G''}$ that relates linear granularities $G''$ and bottom granularity $B$, with $G''$ being aperiodical with respect to $B$, is given by

\begin{equation}\label{eq:eq7}
\begin{split}
A_{B, G''}(z) & = L(1), \quad z \in T_q\\
     & = L(0), \quad z \not\in T_q\\
\end{split}
\end{equation}
where  
$z$ denotes the index set,
$T_q$ are the sets of indices of $B$ describing $G''(q)$ such that $$G''(q) = \bigcup_{z \in T_q}B(z)$$
\end{definition}

 Aperiodic time granularities map a time index to binary categories. It takes a value (eg. 1) whenever the time index coincides with the events in context (e.g. public or school holiday) and another value 0 (e.g. 0) when it does not. \autoref{fig:aperiodic} shows the linear granularity academic semester and days. Academic semesters are not periodic with respect to days. The label mapping L can be defined as $L: ({0,1}) \longmapsto\ ({On, Off)}$ or can be customized based on context.
